Contextuality and Nonlocality in Discrete Quantum Theory

### 2016-02-08 DQC3.tex
"6.1 Gleason's Theorem in DQT" Typed something...

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
\usepackage{amsfonts}
\usepackage{color}
\usepackage{stmaryrd}\usepackage{dsfont}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{enumitem}		% customizable list environments
\newlength{\lyxlabelwidth}      % auxiliary length 
\theoremstyle{plain}
\newtheorem{thm}{\protect\theoremname}
\ifx\proof\undefined
\newenvironment{proof}[1][\protect\proofname]{\par
\normalfont\topsep6\p@\@plus6\p@\relax
\trivlist
\itemindent\parindent
\item[\hskip\labelsep\scshape #1]\ignorespaces
}{%
\endtrivlist\@endpefalse
}
\providecommand{\proofname}{Proof}
\fi
\def\casename{Case. }
 \newlist{casenv}{enumerate}{4}
 \setlist[casenv]{leftmargin=*,align=left,widest={iiii}}
 \setlist[casenv,1]{label={{\itshape\ \casename} \arabic*.},ref=\arabic*}
 \setlist[casenv,2]{label={{\itshape\ \casename} \roman*.},ref=\roman*}
 \setlist[casenv,3]{label={{\itshape\ \casename\ \alph*.}},ref=\alph*}
 \setlist[casenv,4]{label={{\itshape\ \casename} \arabic*.},ref=\arabic*}

@@

Third, even if we require the range of $\hat{\pi}$ has a group structure,
we still may not find $\dpr_{\Psi}=\hat{\pi}$.
%%%%%%%%%%%%%%%%%
\subsection {The Kochen-Specker Theorem in DQT}
The essence of the Kochen-Specker theorem is to ask if it is possible,
for a fixed $\ket{\Psi}\in\ffzd{p^{2}}$, to have another function
$v\left(\ket{\Phi}\right)$ playing the role of
$\dpr \left(\ket{\Psi},\ket{\Phi}\right)$ but failing to satisfy any
single one of the conditions in the set
(\ref{enu:total-probability-DQT(I)},\ref{enu:particular-vector-DQT(I)},
\ref{enu:parallel-DQT(I)},\ref{enu:unitary-DQT(I)}) and to show that
this cannot be true.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
\usepackage{amsfonts}
\usepackage{color}
\usepackage{stmaryrd}\usepackage{dsfont}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{enumitem}		% customizable list environments
\newlength{\lyxlabelwidth}      % auxiliary length 
\theoremstyle{plain}
\newtheorem{thm}{\protect\theoremname}
\ifx\proof\undefined
\newenvironment{proof}[1][\protect\proofname]{\par
\normalfont\topsep6\p@\@plus6\p@\relax
\trivlist
\itemindent\parindent
\item[\hskip\labelsep\scshape #1]\ignorespaces
}{%
\endtrivlist\@endpefalse
}
\providecommand{\proofname}{Proof}
\fi
\def\casename{Case. }
 \newlist{casenv}{enumerate}{4}
 \setlist[casenv]{leftmargin=*,align=left,widest={iiii}}
 \setlist[casenv,1]{label={{\itshape\ \casename} \arabic*.},ref=\arabic*}
 \setlist[casenv,2]{label={{\itshape\ \casename} \roman*.},ref=\roman*}
 \setlist[casenv,3]{label={{\itshape\ \casename\ \alph*.}},ref=\alph*}
 \setlist[casenv,4]{label={{\itshape\ \casename} \arabic*.},ref=\arabic*}
\newtheorem{problem}[thm]{Problem}

@@

If the problem is that the range of $\hat{\pi}$ is only a semigroup,
we may want to consider the range of $\hat{\pi}$ to be a group.
\begin{problem}
\label{thm:GleasonDQT-group}Is there a group $\left(\mathscr{L},0,\oplus\right)$
with a special element $1\in\mathscr{L}$ and $1\ne0$ satisfying
the following statement? 
\begin{itemize}
\item There is a way to define a mixed state $\rho$ and a corresponding
Born rule $\tilde{\pi}_{\rho}:\ffzd{p^{2}}\rightarrow\mathscr{L}$
in a sense of equation (\ref{prob.mixed}).
\item For $d\ge3$, for any $\hat{\pi}:\ffzd{p^{2}}\rightarrow\mathscr{L}$
satisfying 
\begin{eqnarray}
 &  & \textrm{For any vector }\ket{i}\in\ffzd{p^{2}}\textrm{, and }\gamma\in\ff{p^{2}}^{*}\textrm{ , }\hat{\pi}(\ket{i})=\hat{\pi}(\gamma\ket{i})\textrm{ . }\label{eq:parallel-DQT-1}\\
 &  & \textrm{For any orthonormal basis }\{\ket{i}\}\textrm{ , }{\displaystyle \bigoplus_{i=0}^{d-1}\hat{\pi}\left(\ket{i}\right)=}1\textrm{ .}\label{eq:total-probability-DQT-1}
\end{eqnarray}
There is a mixed state $\rho$ such that $\hat{\pi}=\tilde{\pi}_{\rho}$.
\end{itemize}
\end{problem}
When $d=3$ and $p=7$, we have verified that we no longer have the
freedom to assign impossible more than any reasonable probability
assignment. Therefore, we cannot find a similar counterexample for
problem \ref{thm:GleasonDQT-group}. However, even if there is a group
$\left(\mathscr{L},0,\oplus\right)$ satisfying problem \ref{thm:GleasonDQT-group},
the corresponding Born rule $\tilde{\pi}_{\rho}:\ffzd{p^{2}}\rightarrow\mathscr{L}$
is not basis independent, i.e., we will not have 
\begin{equation}
\tilde{\pi}_{U\rho}\left(U\ket{i}\right)=\tilde{\pi}_{\rho}\left(\ket{i}\right)\label{eq:rotation-1}
\end{equation}
for all unitary matrix $U$, mixed state $\rho$, and pure state $\ket{i}\in\ffzd{p^{2}}$,
and the proof is similar to the one of the no-go theorem in section
\ref{sub:A-No-Go-Theorem}.

In summary, there are some difficulties to establish corresponding
Gleason's theorem in DQT no matter how we set the conditions. However,
Gleason's theorem gives an idea how to fine ``the'' reasonable Born
rule in a discrete quantum theory, and we hope we may find one in
the future.

%%%%%%%%%%%%%%%%%
\subsection {The Kochen-Specker Theorem in DQT}
The essence of the Kochen-Specker theorem is to ask if it is possible,
for a fixed $\ket{\Psi}\in\ffzd{p^{2}}$, to have another function
$v\left(\ket{\Phi}\right)$ playing the role of
$\dpr \left(\ket{\Psi},\ket{\Phi}\right)$ but failing to satisfy any
single one of the conditions in the set
(\ref{enu:total-probability-DQT(I)},\ref{enu:particular-vector-DQT(I)},
\ref{enu:parallel-DQT(I)},\ref{enu:unitary-DQT(I)}) and to show that
this cannot be true.
